\roottitle{Experience} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.foundationbaptistcollege.com/}{Foundation Baptist College}}
	{\textsc{Edmonton, \acr{AB}}} {

	\headedsubsection % Job title entry for the current employer
	{Vice President}
	{October 2013 -- present}
	{\bodytext{ Foundation Baptist College is a small, new, non-profit post-secondary education institution that provides vocational training for prospective Christian ministers and personal enrichment courses for Christian adults. My role there included overseeing various aspects of the business affairs of the College while also teaching college courses on the biblical text, theology, and history. Some of my accomplishments included assisting the President and Board of Directors to incorporate the College under the Alberta \textit{Companies Act}, applying for (and successfully obtaining) Charitable Status from \acr{CRA}, working with a Chartered Accountant to obtain audited financial statements for the College's fiscal year, and overseeing the development and release of a new website. }}
}

% \bodytext{Intellecap is a social-sector advisory firm serving corporates, non-profits, development agencies and governments working in developing markets. I assessed their software development team and methodologies, trained their developers and build several web applications. One of those apps is \href{http://www.mostfit.org}{Mostfit}, an open source \acr{MIS} for \href{http://en.wikipedia.org/wiki/Microcredit}{microcredit} lenders.}


%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.meadowlandsbaptist.ca/}{Meadowlands Baptist Church}}
{\textsc{Edmonton, \acr{AB}}} {

\headedsubsection % Job title entry for the current employer
{Church Administrator}
{October 2012 -- September 2013}
{\bodytext{With an average of 500 attendees on a Sunday morning, Meadowlands Baptist Church is a larger church located in southeast Edmonton. My role at the church involved serving as administrative support to the Senior Pastor while also overseeing a variety of church operations. Some of my responsibilities included organizing and overseeing volunteers in various church ministries, overseeing building maintenance staff, participating in meetings with the church pastoral staff and deacon board, and writing curriculum for adult education classes.}
% TODO: finish summary and incorporate into block immediately above.
% Organized, oversaw, and executed routine church operations through support staff and volunteers. Managed church operations, finances, human resources, and projects.

%\bodytext{Dharma Publishing, the worlds largest Buddhist publisher, is a non-profit, all-volunteer organization that helps to preserve Tibetan Buddhism and culture. I build them a \href{http://www.dharmapublishing.com}{web store}, and moved the infrastructure of all their web media to a nearly zero maintenance setup that they can maintain themselves.}
}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.macewan.ca/}{MacEwan University}}
{\textsc{Edmonton, \acr{AB}}} {

\headedsubsection % Job title entry for the current employer
{Technology Support Centre Assistant}
{August 2011 -- October 2012}
{\bodytext{Provided technology support to students, staff and faculty via phone, walk up and e-mail, focusing on end-user support for computer applications and peripherals as well as use of the University network and internet resources.
}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.bju.edu/}{Bob Jones University}}
{\textsc{Greenville, \acr{SC}, \acr{USA}}} {

\headedsubsection % Job title entry for the current employer
{Graduate Assistant, Mack Library}
{May 2006 -- May 2010}
{\bodytext{Abstracted and cataloged popular and scholarly articles on religion, theology, biblical interpretation, ethics, history, and current events while assisting with patron research queries. Supervised student workers working in circulation, periodicals, reference, and shelving during night and weekend shifts. Wrote code to facilitate library projects and processes. Organized, marketed and taught [instructional workshops][semprojworkshops] on the use of various technologies in seminary research. Wrote [online subject guides][libguides] on a variety of topics. Projects included: designing an updated web interface for the library catalog, generating barcode labels for approximately 80,000 items from the Library catalog, fixing a broken reference statistics database, simplifying research processes, as well as various small scripts for inventory processing and data migration.}} %todo: add links


\headedsubsection % Job title entry for the current employer
{Student Lab Monitor, Computer Science Department}
{2004 -- 2006}
{\bodytext{Assisted students with class assignments. Designed an internal website for the Computer Science Department.}}
}

%------------------------------------------------

%\begin{center}
%\textit{Please refer to \href{http://www.linkedin.com/in/ciesbreijs}{my Linkedin profile} for the complete list of work experiences along with recommendations.}
%\end{center}

%------------------------------------------------

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after