\roottitle{Projects}

I have always enjoyed building online projects. A short list of some of my favorites is below, while a more comprehensive list can be found on the \href{http://duncanjohnson.ca/projects/}{``Projects'' page of my website}.

\begin{itemize}
\item \textbf{Bible study worksheets (\href{https://github.com/dtjohnso/bible-study-worksheets}{Github repo}).} I have written study guides for several New Testament books, including John, 1 \& 2 Corinthians, Ephesians, 1 \& 2 Peter, 1--3 John, and Jude (among others).
\item \textbf{Timeline of Old Testament History (\href{http://duncanjohnson.ca/OT-Timeline/}{Website}; \href{https://github.com/dtjohnso/OT-Timeline}{Github repo}).} This timeline covers the history of Old Testament Israel. Because of the massive scope of Old Testament history, there is much more that I'd like to add here someday.
\item \textbf{Student Writing Helps (\href{http://duncanjohnson.ca/Student-Writing-Helps/}{Website}; \href{https://github.com/dtjohnso/Student-Writing-Helps}{Github repo}).} A website to host material I developed for the \textit{Seminary Project Labs} project at BJU. This site guides users through the installation and configuration of Greek and Hebrew fonts, the use of a Turabian template, and Zotero. It includes some of my old screencasts that I made for the original project.
\item \textbf{\href{http://moodle.duncanjohnson.ca/}{moodle.duncanjohnson.ca}} - An installation of the Moodle LMS that I have used with some of my courses.
\item \textbf{\href{http://library.foundationbaptistcollege.com/}{library.foundationbaptistcollege.com}} - Unlike many of my other website projects (which are predominantly deployed on shared hosting), this site is a live install of the open-source \href{https://koha-community.org/}{Koha ILS} on a small Ubuntu server that I maintain. This has been a great experience for me, since I've been able to practice maintaining a small Linux-based server in a low-stakes deployed environment.
\end{itemize}