\roottitle{Summary} % Root section title

\vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content

\begin{multicols}{2}  % Start a two-column layout
\noindent \textit{Young, educated professional with some management experience, seeking new opportunities through a career change into the tech sector.}\\\\

% Goal: write one to three paragraph section here (max 150 words) to support statement above and describe some of the info in the comments about values and skills below

%	Who I am

As a young professional with a diverse background in tech and academia, I have frequently needed to rapidly acquire new skills. This variety of experiences has challenged me to grow in transferable managerial and technological skills while also advancing my knowledge within specific fields of study.

%	What I can bring to the table

With significant public speaking experience, I highly value clear and effective communication. For me, a project is not complete unless it is done well. I place a premium upon my personal character and work ethic. I seek trust and transparency in my personal and professional affairs.

%	My career aim

Presently, my goal is to transition from academia into the tech sector. I want to combine my experience in education with my interest in online technology to create rich experiences for learners. As a learner myself, I want to build on my educational background in software development with rigorous self-education in development best practices to further enhance my technical skills.


\end{multicols}

% \spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after
