\roottitle{Community Service} % Top level section


\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Meadowlands Baptist Church}
{\textsc{Edmonton, AB}} {

\headedsubsection % Job title entry for the current employer
{Adult Sunday School Coordinator}
{2013 -- 2015}
{\bodytext{
Wrote weekly curriculum for adult educational programs.
}}

\headedsubsection % Job title entry for the current employer
{Adult Sunday School Teacher}
{2012 -- present}
{\bodytext{
Prepared and taught weekly expository Bible lessons on a variety of New Testament books.
}}

\headedsubsection % Job title entry for the current employer
{Summer Intern}
{June -- August 2011}
{\bodytext{
Preached and taught in a variety of church services. Assisted with youth activities.
}}
}
%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Foundation Baptist College}
{\textsc{Edmonton, \acr{AB}}} {

\headedsubsection % Job title entry for the current employer
{Professor}
{June 2011 -- September 2013}
{\bodytext{
Taught Bible courses, managed library and maintained college web presence, among other duties.
}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Grace Baptist Church}
{\textsc{Dacula, \acr{GA}, \acr{USA}}} {

\headedsubsection % Job title entry for the current employer
{Volunteer}
{Oct. 2006 -- May 2010}
{\bodytext{
Led bi-weekly Bible studies with a small group. Taught various adult, teen and children's Sunday school classes. Participated in youth group activities as a sponsor. Maintained church website and social network pages. Trained for and managed sound booth equipment.
}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Mt. Calvary Baptist Church}
{\textsc{Greenville, \acr{SC}, \acr{USA}}} {

\headedsubsection % Job title entry for the current employer
{Intern}
{Jan. 2006 -- May 2006}
{\bodytext{
Exposed to and involved in all aspects of church ministry.
}}

}

%------------------------------------------------

% \spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after