\roottitle{Employment Experience} % Top level section
%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://crerarlaw.ca/}{Crerar Law, \acr{LLP}}}
{\textsc{Edmonton, \acr{AB}}} 
{
	\headedsubsection % Job title entry for the current employer
	{Legal Assistant}
	{July 2017 -- present}
	{
		\bodytext{ I assisted lawyers with preparation of legal documents, drafting correspondence, organizing files, and scheduling. Obtained my commission to act as a Commissioner of Oaths in and for Alberta. Acted as IT liaison for the firm, working closely with contractors to resolve issues with the firm's network and server (Exchange running on an ESXi HyperV) and end-user desktops. }
	}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.foundationbaptistcollege.com/}{Foundation Baptist College}}
{\textsc{Edmonton, \acr{AB}}} 
{
	\headedsubsection % Job title entry for the current employer
	{Professor and Registrar}%{Vice President}
	{October 2013 -- May 2017}
	{
		\bodytext{ Foundation Baptist College is a small, non-profit post-secondary education institution that provides vocational training for prospective Christian ministers and personal enrichment courses for Christian adults. I oversaw various aspects of the academic and business affairs of the College and taught college courses on the biblical text, theology, and history. Serving as Registrar, I managed course scheduling and registration while serving as academic advisor for the majority of the College's credit students. Some of my other accomplishments included overseeing a successful fund-raising drive that brought in over \$100,000, incorporating the College under the Alberta \textit{Companies Act}, obtaining Charitable Status from the Canada Revenue Agency, producing audited financial statements for the College's first fiscal year, overseeing the development and release of a new Wordpress-powered website, launching an online catalog for the College library, and overseeing the cataloging of the library collection. }
	}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.meadowlandsbaptist.ca/}{Meadowlands Baptist Church}}
{\textsc{Edmonton, \acr{AB}}} 
{
	\headedsubsection % Job title entry for the current employer
	{Church Administrator}
	{October 2012 -- September 2013}
	{
		\bodytext{With an average of 500 Sunday-morning attenders, Meadowlands Baptist Church is a larger church in southeast Edmonton. I provided administrative support to the Senior Pastor while also overseeing a variety of church operations. Some of my responsibilities included organizing and overseeing volunteers in various ministries, overseeing building maintenance staff, participating in meetings with the pastoral staff and deacon board, and writing curriculum for adult education classes.}
	}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.macewan.ca/}{MacEwan University}}
{\textsc{Edmonton, \acr{AB}}} 
{

	\headedsubsection % Job title entry for the current employer
	{Technology Support Centre Assistant}
	{August 2011 -- October 2012}
	{
		\bodytext{I provided Tier 1 technology support to students, staff and faculty via phone, walk up and e-mail, focusing on end-user support for computer applications and peripherals as well as use of the University network and internet resources.}
	}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.bju.edu/}{Bob Jones University}}
{\textsc{Greenville, \acr{SC}, \acr{USA}}} 
{

	\headedsubsection % Job title entry for the current employer
	{Graduate Assistant, Mack Library}
	{May 2006 -- May 2011}
	{
		\bodytext{ 
			The Mack Library is the primary academic library for the Bob Jones University community. As a graduate assistant, I carried out a number of ongoing duties while also assisting with special projects. My primary task was to abstract and catalog popular and scholarly articles stored in the \href{http://libguides.bju.edu/ffile}{Fundamentalism File}, which is a resource center with over 118,000 items of information classified under 5,000 different subjects. Topics covered in this collection include religion, theology, biblical interpretation, ethics, history, and current events. I assisted students, faculty, and guests with research queries and supervised library student workers on nights and weekend shifts. Some of my projects included organizing, marketing, and teaching instructional workshops on the use of technology in student research; designing an updated web interface for the library catalog; writing a variety of online subject guides; and generating barcode labels for approximately 80,000 items using data from the library catalog.
			% fixing a broken reference statistics database, simplifying research processes, as well as various small scripts for inventory processing and data migration. 
		}
	}

	% \headedsubsection % Job title entry for the current employer
	% {Student Lab Monitor, Computer Science Department}
	% {2004 -- 2006}
	% {
	% 	\bodytext{Assisted students with class assignments. Designed an internal website for the Computer Science Department.}
	% }
}

%------------------------------------------------

% LINKEDIN REFERENCE

%\begin{center}
%\textit{Please refer to \href{http://www.linkedin.com/in/ciesbreijs}{my Linkedin profile} for the complete list of work experiences along with recommendations.}
%\end{center}

%------------------------------------------------

% \spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is afte